---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Computing Simultaneous Confidence Bands in R

Simultaneous confidence bands are versatile tools for visualizing estimation uncertainty for parameter vectors ([Montiel Olea and Plagborg-Møller 2019](https://doi.org/10.1002/jae.2656)). 

This repo houses a [R](https://www.r-project.org/) package that computes the critical values underlying the simultaneous sup-t confidence bands proposed in [Montiel Olea and Plagborg-Møller (2019)](https://doi.org/10.1002/jae.2656). 

## Installation

You can install the package from [GitHub](https://github.com/):

``` r
# install.packages("devtools")
devtools::install_github("ryanedmundkessler/suptCriticalValue")
```

The following example shows how to calculate sup-t critical values and, in turn, construct sup-t confidence bands:

```{r}
library(suptCriticalValue)
library(MASS)
data(Cars93, package = "MASS")
conf_level  <- 0.95
model       <- lm(Price ~ Weight + Wheelbase + Cylinders, data=Cars93)

beta        <- matrix(coef(model))
vcov_matrix <- vcov(model)
std_error   <- sqrt(diag(vcov_matrix))

pw_crit     <- qt(1 - ((1 - conf_level) / 2), model$df.residual) 
supt_crit   <- suptCriticalValue(vcov_matrix = vcov_matrix)

pw_ci_lb    <- beta - pw_crit * std_error 
pw_ci_ub    <- beta + pw_crit * std_error 
supt_ci_lb  <- beta - supt_crit * std_error 
supt_ci_ub  <- beta + supt_crit * std_error 

print("POINTWISE 95 PERCENT CONFIDENCE INTERVAL: ")
print(paste0(
  "[", pw_ci_lb, ", ", pw_ci_ub, "]"
))

print("SIMULTANEOUS SUP-T 95 PERCENT CONFIDENCE INTERVAL: ")
print(paste0(
  "[", supt_ci_lb, ", ", supt_ci_ub, "]"
))
```

## Unit Tests

[`monte_carlo.R`](./inst/test/code/monte_carlo.R) asserts that the resulting sup-t confidence bands have expected coverage under select data generating processes 

## Author

Ryan Kessler
<br>Email: ryan.edmund.kessler@gmail.com

## License

This project is licensed under the MIT License. See the [LICENSE.md](LICENSE.md) file for details

## References

Montiel Olea, José Luis and Mikkel Plagborg-Møller. 2019. Simultaneous Confidence Bands: Theory, Implementation, and an Application to SVARs. Journal of Applied Econometrics. https://doi.org/10.1002/jae.2656
